discussion

### 2018-05-07 man/ms_2_results.Rmd
new update
update results and discussion

Likely as a consequence of their different management origin (*i.e.* land-use legacy), the trees of the southern population were older than northern ones, particularly for the high elevation site (CA-High) which had bigger and taller trees than the other sites (Tables 1, 2). The competition index was similar among sites but plot basal area was greatest in CA-High (Table 1). Yet the basal area increment (BAI) growth in the highest plot in altitude (CA-High) was the greatest (Figure 4). Trees from this location showed in addition a positive growth trend since the late 1970s (Figure 4). This positive trend was not found in any of the other two locations and the two altitudes sampled in the southern populations showed differences in growth, being more similar CA-Low with growth in the northern population (SJ) than with CA-High (Figure 4; Appendix S7).

@@

The exploration of resilience metrics of tree-growth for other severe droughts, revealed a positive relation between resilience (*Rs*) and drought severity ($r^2$ = 0.336) (Appendix S6). A similar pattern was found for recovery (*Rc*; $r^2$ = 0.438) but negative for resistance (*Rt*, $r^2$ = 0.155). Resilience values of tree-growth for 2005 was the lowest of the drought events analyzed (Appendix S6) even not being the most severe drought events.

>>>>

Likely as a consequence of their different management origin (*i.e.* land-use legacy), the trees of the southern population were older than northern ones, particularly for the high elevation site (CA-High) which had bigger and taller trees than the other sites (Tables 1, 2). Competition was similar among sites but plot basal area was greatest in CA-High (Table 1). Yet the basal area increment (BAI) growth in the highest plot in altitude (CA-High) was the greatest (Figure 4). In addition, trees from this location showed a positive growth trend since the late 1970s (Figure 4), which was not found for any of the other two locations. For southern population differences in growth were observed, with CA-Low site showing lower values than CA-High but similar to growth values of the northern population (SJ) (Figure 4; Appendix S7).

@@

The exploration of resilience metrics of tree-growth for other severe droughts, revealed a positive relation between resilience (*Rs*) and drought severity ($r^2$ = 0.336) (Appendix S6). A similar pattern was found for recovery (*Rc*; $r^2$ = 0.438) but negative for resistance (*Rt*, $r^2$ = 0.155). Resilience values of tree-growth for 2005 was the lowest of the drought events analyzed (Appendix S5) even not being the most severe drought events.

### 2018-05-07 man/ms_3_discussion.Rmd
update results and discussion

```{r, echo=FALSE}
show_text <- FALSE
```

@@

For tree-growth, a similar positive trend was observed in the last decades, particularly for the southern high-elevation site (CA-High, Figure 4). This result differs from those previous reported for *Q. pyrenaica* along their distribution range [@GeaIzquierdo2013; @GeaIzquierdo2014]. [@GeaIzquierdo2014] found a general decline in the growth of this species since the 1970s, particularly sharp for populations located in their dry-edge. This decline trend in growth have also been oberved for other tree species located in their rear-edges [*e.g.* @SanchezSalguero2012; @SanchezSalguero2017; @Dorado2017]. Furthermore, growth projections have forecasted a decrease in productivity for *Q. pyrenaica* that would increase vulnerability of this species to climate warming at the dry edges locations [@GeaIzquierdo2013]. However, our results for similar locations have revealed a recovery in tree-growth for the last years (Figure 4).

@@

Despite similar value of competence in all sites, we obtained higher values of growth for the highest elevation site (CA-High, Figure 4).

>>>>

```{r, echo=FALSE}
show_text <- FALSE
```
# Discussion

@@

For tree-growth, a similar positive trend was observed in the last decades, particularly for the southern high-elevation site (CA-High, Figure 4). This result differs from those previous reported for *Q. pyrenaica* along their distribution range [@GeaIzquierdo2013; @GeaIzquierdo2014]. @GeaIzquierdo2014 found a general decline in the growth of this species since the 1970s, particularly sharp for populations located in their dry-edge. This decline trend in growth have also been oberved for other tree species located in their rear-edges [*e.g.* @SanchezSalguero2012; @SanchezSalguero2017; @Dorado2017]. Furthermore, growth projections have forecasted a decrease in productivity for *Q. pyrenaica* that would increase vulnerability of this species to climate warming at the dry edges locations [@GeaIzquierdo2013]. However, our results for similar locations have revealed a recovery in tree-growth for the last years (Figure 4).

@@

Despite similar value of competence in our study sites, we obtained higher values of growth for the highest elevation site (CA-High, Figure 4).
